Toy Transit Surveys

### 2017-08-30 memos/workdir/toy_analytic_surveys.tex
finished updating memo with correction factor

Finally, we perform a synthetic transit survey analogous to {\it Kepler}. We 
show that if we assume every star in this {\it Kepler} survey analog is single, 
we underestimate occurrence rates for a given planet radius and period by 
$\approx 39\%$.
This is immediately applicable to the question of Earth-like planets around 
Sun-like stars.

@@

For the completeness term, an argument that I don't wholly believe
is that
\begin{equation}
\frac{f_{c,d1}(R_p')}{f_c(R_p')} = \frac{f_{c,d1}(R_p')}{f_{c,s}(R_p')} \cdot
	\frac{f_{c,s}(R_p')}{f_{c}(R_p')} \lessapprox 1 \cdot (1+\langle \gamma_R 
	\rangle)^3,
\end{equation}
where the first part of the inequality is obvious, but the second is by 
assuming it's $\lessapprox f_{s,c}/f_{d,c}$, which might be wrong because of 
the radius dependence.

@@

\begin{figure}[!t]
	\begin{center}
		\includegraphics[scale=.8]{figures/XGamma_vs_xi.pdf}
	\end{center}
	\caption{\textit{Y axis}: correction factor for the astronomer who 
	ignores binarity but counts planetary radii that are ``close enough'' (A') 
	and the astronomer who knows everything (D).
	\textit{X axis}: $\chi$ as defined in Eq.~\ref{eq:chi_simplified}. Taking a 
	guess at the true value, if $N_{d1}(R_p') = N_d/2$, and the occurrence rates 
	between `d1' and `s' are the same, and we put $\gamma_R = 0.1$ into the 
	completeness ratio, then $\xi = (\beta/2) \times (1+0.1)^{-3} = 0.22$. The 
	relative error then varies between $\approx 5\% - 35\%$, depending on what 
	fraction of secondaries you assume host planets.
		}
	\label{fig:XGamma_vs_xi}
\end{figure}

@@

Similar to Fig.~\ref{fig:XGamma_vs_xi}, Fig.~\ref{fig:error_vs_occrate} 
shows that the magnitude of the relative error 
made by the $\Gamma_{{\rm A},R_p'}$ and $\Gamma_{{\rm A},R_p}$ estimates 
depends strongly 
on the fraction of secondaries that are assumed to host the $(R_p, P)$ planets.
The simplest assumption is that the occurrence rate is the same for all solar 
type stars: any ``Sun-like'' ($0.7<M_\star/M_\odot<1.3$) star hosts planets at 
the ``true rate'' $\Gamma_t$, and any other mass of star does not.
Given how we have defined the GIC, this means that all single stars and 
primaries of double star systems are sun-like. The fraction of Sun-like 
secondaries in this case is 37.4\% of all secondaries.
Reading the appropriate value off Fig.~\ref{fig:error_vs_occrate}, this 
corresponds to $\Gamma_{\rm D} = 1.39 \Gamma_{\rm A'}$.

>>>>

Finally, we perform a synthetic transit survey analogous to {\it Kepler}. We 
show that if we assume every star in this {\it Kepler} survey analog is single, 
we underestimate occurrence rates for a given planet radius and period by 
a factor of $\approx 1.4$, or a percentage error relative to the true 
occurrence rate $\Gamma$ of $\delta\Gamma=-28\%$.
This is relevant for measuring accurate values of the rate at which Earth-like 
planets exist around Sun-like stars.

@@

For the completeness term, an argument that I don't wholly believe
is that
\begin{equation}
\frac{f_{c,d1}(R_p')}{f_c(R_p')} = \frac{f_{c,d1}(R_p')}{f_{c,s}(R_p')} \cdot
	\frac{f_{c,s}(R_p')}{f_{c}(R_p')} \lesssim 1 \cdot (1+\langle \gamma_R 
	\rangle)^3,
\end{equation}
where the first part of the inequality is obvious, but the second is by 
assuming it's $\lesssim f_{s,c}/f_{d,c}$, which might be wrong because of 
the radius dependence.

@@

\begin{figure}[!t]
	\begin{center}
		\includegraphics[scale=.8]{figures/XGamma_vs_xi.pdf}
	\end{center}
	\caption{\textit{Y axis}: correction factor for the astronomer who 
	ignores binarity but counts planetary radii that are ``close enough'' (A') 
	and the astronomer who knows everything (D).
	\textit{X axis}: $\chi$ as defined in Eq.~\ref{eq:chi_simplified}.
	}
	\label{fig:XGamma_vs_xi}
\end{figure}

@@

Similar to Fig.~\ref{fig:XGamma_vs_xi}, Fig.~\ref{fig:error_vs_occrate} 
shows that the magnitude of the correction needed by the $\Gamma_{{\rm 
A},R_p'}$ estimate depends strongly 
on the fraction of secondaries that are assumed to host the $(R_p, P)$ planets.
The simplest assumption is that the occurrence rate is the same for all solar 
type stars: any ``Sun-like'' ($0.7<M_\star/M_\odot<1.3$) star hosts planets at 
the ``true rate'' $\Gamma_t$, and any other mass of star does not.
Given how we have defined the GIC, this means that all single stars and 
primaries of double star systems are sun-like. The fraction of Sun-like 
secondaries in this case is 37.4\% of all secondaries.
Reading the appropriate value off Fig.~\ref{fig:error_vs_occrate}, this 
corresponds to $\Gamma_{\rm D} = 1.39 \Gamma_{\rm A'}$.
This gives a relative percentage error of $\delta\Gamma_{{\rm D},R_p} \equiv 
(\Gamma_{\rm A,R_p'} - \Gamma_{\rm D,R_p}) / \Gamma_{\rm D,R_p} = -28\%$.
